Quasi-Monte Carlo Methods: What, Why, and How?

### 2024-10-23 HickernellMCQMC2024_QMCTutorial.tex
M3 Mac updates

@@

\mainmatter              % start of a contribution
%
\title{Quasi-Monte Carlo Methods:  What, Why, and How?}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Fred J. Hickernell\inst{1} \and Aleksei G. Sorokin\inst{2}}
%
\authorrunning{Hickernell and Sorokin} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Fred J. Hickernell, Aleksei G. Sorokin}
%
\institute{Departmet of Applied Mathematics, Illinois Institute of Technology, Chicago, IL, 60616, USA\\
\email{hickernell@iit.edu}, \ 
\texttt{http://www.iit.edu/~hickernell}
\and
Departmet of Applied Mathematics, Illinois Institute of Technology, Chicago, IL, 60616, USA\\
\email{asorokin@hawk.iit.edu}}

@@

\keywords{}
\end{abstract}
%
\section{Introduction} \label{sec:intro}
%
%
\section{Where in Practice} \label{sec:practice}
\section{Low Discrepancy Sequence Constructions} \label{sec:construct}
\section{Discrepancy} \label{sec:discrepancy}
\section{Stopping Criteria} \label{sec:stop}
\section{Reformulating Our Problem} \label{sec:reformulate}
\section{Ongoing Research} \label{sec:onging}
\section{Conclusion} \label{sec:conclusion}

>>>>

%%Fred's temporary macros

%%End of Fred's temporary macros

@@

\mainmatter              % start of a contribution
%
\title{Quasi-Monte Carlo Methods:  What, Why, and How?}
%
\titlerunning{Quasi-Monte Carlo Methods}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Fred J. Hickernell\inst{1} \and Aleksei G. Sorokin\inst{2}}
%
\authorrunning{Hickernell and Sorokin} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Fred J. Hickernell, Aleksei G. Sorokin}
%
\institute{Departmet of Applied Mathematics, Illinois Institute of Technology, Chicago, IL, 60616, USA\\
\email{hickernell@iit.edu}, \ 
\texttt{http://www.iit.edu/~hickernell}
\and
Departmet of Applied Mathematics, Illinois Institute of Technology, Chicago, IL, 60616, USA\\
\email{asorokin@hawk.iit.edu}}

@@

\keywords{}
\end{abstract}
%
\section{Introduction} \label{sec:intro}
There are may settings where key quantities are unknown, such as future financial market forces, the porosity of rock containing oil or gas, or particle interactions leading to observations in a high energy physics experiment.   Such situations are often modeled using random variables or stochastic processes.  Computations are performed by generating a multidude of scenarios informed by the assumed probability distribution. One may then estimate the mean outcome, quantiles, and distributions.  This is the essence of the Monte Carlo method.

In mathematical terms, the outcome is $Y := f(\boldsymbol{X})$, where $\boldsymbol{X}$ is a vector random variable driving the outcome, and $f$ is a function whose values can be computed by an algorithm, whose complexity may be such that it can be considered a ``black box''.  The scenarios are the $\bsX_0, \bsX_1, \ldots$ that give rise to $Y_0 = f(\bsX_0), Y_1 = f(\bsX_1), \ldots$.  The $Y_i$ form the basis for approximating $\bbE(Y)$ and other quantities of interest.

How one generates scenarios
%
\section{Where in Practice} \label{sec:practice}
\section{Low Discrepancy Sequence Constructions} \label{sec:construct}
\section{Discrepancy} \label{sec:discrepancy}
\section{Stopping Criteria} \label{sec:stop}
\section{Reformulating Our Problem} \label{sec:reformulate}
\section{Ongoing Research} \label{sec:onging}
\section{Conclusion} \label{sec:conclusion}
